\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}
\centering{\textbf{Computer Vision - Assignment 3}}
\newline  Michal Sinai, Oded Golden
\begin{enumerate}
\item Homography: Let $(p_1,p_2,...,p_n)$ be points in image $I_1$ and $(q_1,q_2,...,q_n)$ be points in image $I_2$. We will prove that there exists a 3x3 matrix $H$ such that $\forall i\in [1,n]: p_i=Hq_i$
\begin{enumerate}
\item Assumption: $I_1$ has the same coordinates system as the world.
\item Given: $C=COP_1=COP_2$
\item Let $M_1$ denote the camera calibration matrix of $I_1$ and $M_2$ denote the camera calibration matrix of $I_2$.
\item We can then express any point $P$ from $A$ as $p=M_1P, q=M_2P$
\item From (a) and (b) we get that $p=M_1*P=M_{int}*Projection*P$ and $q=M_2*P=M_{int}*Projection*Rotation_2*P$
\item Let $P'=Projection*P$ denote the projected point of $P$, then $p=M_{int}*P'$ and $q=M_{int}*R_2*P'$
\item Since both $M_{int}$ and $M_{int}*R_2$ are 3x3 matrices, then $p=M_{int}*[M_{int}*R_2]'*q$
\item The homography is $H=M_{int}*[M_{int}*R_2]'$
\end{enumerate}
\item Detect the ground plane in a sequence using the optical flow:
\begin{enumerate}
\item Assumption: points on the ground plane have relatively the same optical flow orientation.
\item Method:
\begin{itemize}
\item Build an histogram from the orientation (the $O$) matrix.
\item For every point with the common $O$ value - color it as the ground plane.
\end{itemize}

\end{enumerate}

\item Determine whether the camera is only rotating using the optical flow:
\begin{enumerate}
\item Assumption: If the camera is only rotating, then if the scene is static - all the points in the image have relatively the same optical flow orientation.
\item Method:
\begin{itemize}
\item Build an histogram from the orientation (the $O$) matrix.
\item If the histogram "looks like" a spike - the camera is only rotating. That is, if the common value of $O$ appears more than the second common by a factor of $k$, where $k$ is our threshold.
\end{itemize}

\end{enumerate}

\end{enumerate}

\end{document}
